% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
\documentclass[
]{article}
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{longtable,booktabs,array}
\newcounter{none} % for unnumbered tables
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
% pdf_header.tex — Unicode-to-LaTeX mappings for pandoc/xelatex builds
% Used by build_pdfs.sh for ManyClocks.pdf and Equations.pdf.
% Maps prose-mode Unicode characters (Greek letters, math symbols, arrows,
% blackboard bold, etc.) to LaTeX commands so they render correctly in
% paragraphs, captions, and tables — outside of $...$ math mode where
% the math font would normally handle them.

\usepackage{newunicodechar}
\usepackage{amsmath,amssymb}
\newunicodechar{ℏ}{\ensuremath{\hbar}}
\newunicodechar{⟨}{\ensuremath{\langle}}
\newunicodechar{⟩}{\ensuremath{\rangle}}
\newunicodechar{→}{\ensuremath{\rightarrow}}
\newunicodechar{←}{\ensuremath{\leftarrow}}
\newunicodechar{↔}{\ensuremath{\leftrightarrow}}
\newunicodechar{⇒}{\ensuremath{\Rightarrow}}
\newunicodechar{⇔}{\ensuremath{\Leftrightarrow}}
\newunicodechar{≈}{\ensuremath{\approx}}
\newunicodechar{≠}{\ensuremath{\neq}}
\newunicodechar{≤}{\ensuremath{\leq}}
\newunicodechar{≥}{\ensuremath{\geq}}
\newunicodechar{≪}{\ensuremath{\ll}}
\newunicodechar{≫}{\ensuremath{\gg}}
\newunicodechar{∝}{\ensuremath{\propto}}
\newunicodechar{∼}{\ensuremath{\sim}}
\newunicodechar{√}{\ensuremath{\surd}}
\newunicodechar{∞}{\ensuremath{\infty}}
\newunicodechar{∂}{\ensuremath{\partial}}
\newunicodechar{∇}{\ensuremath{\nabla}}
\newunicodechar{∫}{\ensuremath{\int}}
\newunicodechar{∑}{\ensuremath{\sum}}
\newunicodechar{∈}{\ensuremath{\in}}
\newunicodechar{∉}{\ensuremath{\notin}}
\newunicodechar{⊗}{\ensuremath{\otimes}}
\newunicodechar{⊕}{\ensuremath{\oplus}}
\newunicodechar{·}{\ensuremath{\cdot}}
\newunicodechar{×}{\ensuremath{\times}}
\newunicodechar{±}{\ensuremath{\pm}}
\newunicodechar{✓}{\ensuremath{\checkmark}}
\newunicodechar{ψ}{\ensuremath{\psi}}
\newunicodechar{Ψ}{\ensuremath{\Psi}}
\newunicodechar{φ}{\ensuremath{\varphi}}
\newunicodechar{Φ}{\ensuremath{\Phi}}
\newunicodechar{χ}{\ensuremath{\chi}}
\newunicodechar{σ}{\ensuremath{\sigma}}
\newunicodechar{Σ}{\ensuremath{\Sigma}}
\newunicodechar{α}{\ensuremath{\alpha}}
\newunicodechar{β}{\ensuremath{\beta}}
\newunicodechar{γ}{\ensuremath{\gamma}}
\newunicodechar{δ}{\ensuremath{\delta}}
\newunicodechar{Δ}{\ensuremath{\Delta}}
\newunicodechar{ε}{\ensuremath{\varepsilon}}
\newunicodechar{ω}{\ensuremath{\omega}}
\newunicodechar{Ω}{\ensuremath{\Omega}}
\newunicodechar{η}{\ensuremath{\eta}}
\newunicodechar{θ}{\ensuremath{\theta}}
\newunicodechar{Θ}{\ensuremath{\Theta}}
\newunicodechar{ν}{\ensuremath{\nu}}
\newunicodechar{ρ}{\ensuremath{\rho}}
\newunicodechar{τ}{\ensuremath{\tau}}
\newunicodechar{λ}{\ensuremath{\lambda}}
\newunicodechar{Λ}{\ensuremath{\Lambda}}
\newunicodechar{μ}{\ensuremath{\mu}}
\newunicodechar{π}{\ensuremath{\pi}}
\newunicodechar{Π}{\ensuremath{\Pi}}
\newunicodechar{ξ}{\ensuremath{\xi}}
\newunicodechar{ζ}{\ensuremath{\zeta}}
\newunicodechar{κ}{\ensuremath{\kappa}}
\newunicodechar{ℓ}{\ensuremath{\ell}}
\newunicodechar{ℝ}{\ensuremath{\mathbb{R}}}
\newunicodechar{ℂ}{\ensuremath{\mathbb{C}}}
\newunicodechar{ℕ}{\ensuremath{\mathbb{N}}}
\newunicodechar{ℤ}{\ensuremath{\mathbb{Z}}}
\newunicodechar{²}{\textsuperscript{2}}
\newunicodechar{³}{\textsuperscript{3}}
\newunicodechar{¹}{\textsuperscript{1}}
\newunicodechar{₀}{\textsubscript{0}}
\newunicodechar{₁}{\textsubscript{1}}
\newunicodechar{₂}{\textsubscript{2}}
\newunicodechar{⁻}{\textsuperscript{-}}
\newunicodechar{⁰}{\textsuperscript{0}}
\newunicodechar{⁴}{\textsuperscript{4}}
\newunicodechar{⁵}{\textsuperscript{5}}
\newunicodechar{⁶}{\textsuperscript{6}}
\newunicodechar{⁷}{\textsuperscript{7}}
\newunicodechar{⁸}{\textsuperscript{8}}
\newunicodechar{⁹}{\textsuperscript{9}}
\newunicodechar{ᵃ}{\textsuperscript{a}}
\newunicodechar{ᵇ}{\textsuperscript{b}}
\newunicodechar{−}{$-$}
\newunicodechar{—}{---}
\newunicodechar{–}{--}
\newunicodechar{…}{\ldots}
\newunicodechar{′}{\ensuremath{'}}
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  colorlinks=true,
  linkcolor={Maroon},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

{
\setcounter{tocdepth}{2}
\tableofcontents
}
\section{Equation Reference for the Many Clocks
Interpretation}\label{equation-reference-for-the-many-clocks-interpretation}

\emph{Kuramoto synchronization in the Dirac equation --- the equation
reference accompanying the Many Clocks Interpretation of Quantum
Mechanics (MCI). See the main paper for the interpretive framework; this
document is a compact lookup of the key equations and identifications.}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{0. Note on Bases}\label{note-on-bases}

Two decompositions of the same 4-component Dirac spinor appear below:

\begin{itemize}
\tightlist
\item
  \textbf{Weyl (chiral) basis} ψ = (ψ\_L, ψ\_R)ᵀ --- used in §§2, 5, 6,
  8, 16. The mass term is off-diagonal, so K = m reads as a coupling
  between two chiral clocks.
\item
  \textbf{Dirac (standard) basis} ψ = (ψ\_upper, ψ\_lower)ᵀ = (large,
  small)ᵀ --- used in §4 and the three-term block decomposition E\_LL +
  E\_SS + E\_LS. The spinor u(p,↑) = N(1, 0, r, 0)ᵀ lives here, with r =
  p/(E+m).
\end{itemize}

The two are unitarily related. They agree at θ\_rel = 0 (rest: ψ\_L =
ψ\_R, small = 0) and θ\_rel = π/2 (massless: chiral decoupling =
large/small decoupling). At intermediate momenta the temporal-phase
content is a θ\_rel-dependent mixture in either basis. The interpretive
identifications ``temporal clock'' and ``spatial clock'' are anchored to
ψ\_L and ψ\_R respectively; the large/small split is the basis the block
decomposition lives in.

See PAPER\_UNIFIED.md §2.1.1 for the full discussion.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{1. The Time-Phase Wave
Function}\label{the-time-phase-wave-function}

The Schrödinger equation --- which never collapses:

\[i\hbar \frac{\partial \psi}{\partial t} = \hat{H}\psi\]

The wave function augmented with an explicit internal clock phase
\(\varphi\):

\[\psi_A(\mathbf{x}, t) = \sum_s c_s |s\rangle \cdot e^{-i\omega t + i\varphi_A(t)}\]

where \(\omega = E/\hbar\) is the particle's clock frequency and
\(\varphi_A(t)\) is its internal clock phase --- distinct from the
dynamical phase \(-i\omega t\).

The probability of detecting a property along axis \(\hat{n}\) depends
on the \textbf{relative phase} between particle clock and detector
clock:

\[P\!\left(+1 \,\middle|\, \hat{n},\, \varphi_A,\, \Phi_D\right) = \cos^2\!\left(\frac{\varphi_A - \Phi_D - \theta_{\hat{n}}}{2}\right)\]

\textbf{Entanglement} is synchronized clocks at creation:

\[\varphi_A(0) = \varphi_B(0) = \varphi_0 \qquad \text{(shared initial phase)}\]

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{2. Kuramoto Phase
Synchronization}\label{kuramoto-phase-synchronization}

The equation governing clock synchronization --- the mechanism of
measurement:

\[\frac{d\varphi}{dt} = \omega + K \sin(\Phi_{\text{bulk}} - \varphi)\]

\begin{itemize}
\tightlist
\item
  Free flight:
  \(K = 0 \;\Rightarrow\; \varphi(t) = \varphi_0 + \omega t\) (clocks
  run freely)
\item
  At detector: \(K > 0 \;\Rightarrow\; \varphi \to \Phi_{\text{bulk}}\)
  (synchronization)
\end{itemize}

Fixed point of synchronization: \(\varphi^\star = \Phi_{\text{bulk}}\).
Time to lock: \(\tau_{\text{sync}} = 1/K\).

The detector's clock phase is pre-established by thermal equilibration
with the macroscopic environment:

\[\Phi_{D_1} = \Phi_{D_2} = \Phi_{\text{bulk}} \qquad \text{(both detectors, before the experiment)}\]

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{3. Bell's Theorem --- Where the Factorization
Fails}\label{bells-theorem-where-the-factorization-fails}

Bell's hidden variable theorem writes:

\[E(a, b) = \int A(a,\lambda)\, B(b,\lambda)\, \rho(\lambda)\, d\lambda\]

with two embedded assumptions:

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.3333}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.3333}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.3333}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Assumption
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Standard form
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Status in this model
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Locality & \(A\) depends only on \((a, \lambda)\) & Satisfied --- each
detector is local \\
Measurement independence & \(\rho(\lambda \mid a,b) = \rho(\lambda)\) &
\textbf{Fails} --- \(\Phi_{\text{bulk}} \in \lambda\) is shared \\
\end{longtable}
}

The hidden state in this model is
\(\lambda = (\varphi_0, \Phi_{\text{bulk}})\). Because
\(\Phi_{\text{bulk}}\) is \textbf{the same variable} at both detectors,
the joint distribution does not factorize:

\[\rho(\varphi_0, \Phi_{\text{bulk}}) \;\neq\; \rho(\varphi_0) \cdot \rho(\Phi_{\text{bulk}})\]

This is not a conspiracy. It is ordinary thermodynamic equilibration,
established locally and subliminally before the experiment runs.

\subsubsection{Correlation functions
compared}\label{correlation-functions-compared}

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.3333}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.3333}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.3333}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Model
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\(E(a, b)\)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
CHSH\(_{\max}\)
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Classical LHV (deterministic) &
\(-\!\left(1 - \dfrac{2|\Delta|}{\pi}\right)\) & \(2.000\) \\
Phase-clock (Malus law) & \(-\tfrac{1}{2}\cos\Delta\) &
\(\sqrt{2} \approx 1.414\) \\
Standard quantum mechanics & \(-\cos\Delta\) &
\(2\sqrt{2} \approx 2.828\) \\
\end{longtable}
}

where \(\Delta = a - b\). The phase-clock model is sub-classical in
isolation; the full quantum result requires the Dirac structure below.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{4. Dirac Spinors as Time-Phase / Property
Rotation}\label{dirac-spinors-as-time-phase-property-rotation}

This section uses the Dirac/standard basis (large/small blocks); the
Weyl-basis description of the same spinor appears in §6. See §0 for the
relationship between the two bases.

For a particle with 3-momentum \(p\) along \(z\) (natural units
\(m = c = \hbar = 1\)):

\[u(p, \uparrow) = N \begin{pmatrix} 1 \\ 0 \\ r \\ 0 \end{pmatrix}, \qquad u(p, \downarrow) = N \begin{pmatrix} 0 \\ 1 \\ 0 \\ -r \end{pmatrix}\]

where \(r = \dfrac{p}{E + m}\) and \(N = \sqrt{\dfrac{E+m}{2E}}\).

The \textbf{mixing angle} between temporal and spatial clock vectors:

\[\tan\frac{\theta_{\text{rel}}}{2} = \frac{|\mathbf{p}|}{E + m} \qquad \Longleftrightarrow \qquad \sin\theta_{\text{rel}} = \frac{v}{c}\]

Limits:

\[\theta_{\text{rel}} \xrightarrow{v/c \to 0} 0 \quad \text{(NR: 2-component Pauli suffices)}\]

\[\theta_{\text{rel}} \xrightarrow{v/c \to 1} \frac{\pi}{2} \quad \text{(massless: permanent orthogonality)}\]

\subsubsection{Three-term block decomposition of the Bell
correlation}\label{three-term-block-decomposition-of-the-bell-correlation}

By restricting the Dirac spin operator to the upper (large), lower
(small), and cross blocks, the singlet correlation partitions as:

\[E(a, b) = \underbrace{E_{LL}}_{\text{temporal} \times \text{temporal}} + \underbrace{E_{SS}}_{\text{spatial} \times \text{spatial}} + \underbrace{E_{LS}}_{\text{rotation coupling}} = -\cos(a - b)\]

The sum is additive by trace linearity --- an identity, not a
derivation. The mathematical content is the \emph{redistribution} of
weight among the three blocks as \(\theta_{\text{rel}}\) varies: at
\(p \to 0\), \(E_{LL} \to -\cos(a-b)\) and \(E_{SS}, E_{LS} \to 0\)
(recovering the standard Pauli singlet); at
\(\theta_{\text{rel}} \to 90°\) the three contributions become
comparable. The Malus-law toy in the table above (CHSH
\(\leq \sqrt{2}\), returning \(-\tfrac{1}{2}\cos\Delta\)) is a separate
stochastic-phase model --- it is not the same object as the Dirac
large-block restriction.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{5. Massless Spin-½ Fermions --- Permanent Chiral
Orthogonality}\label{massless-spin-uxbd-fermions-permanent-chiral-orthogonality}

For \(m = 0\) in the Dirac equation: \(\theta_{\text{rel}} = \pi/2\)
always. The equation splits into two independent Weyl equations:

\[i\sigma^\mu \partial_\mu \chi_R = 0 \qquad \text{(spatial clock: helicity } h = +\tfrac{1}{2}\text{)}\]

\[i\bar{\sigma}^\mu \partial_\mu \chi_L = 0 \qquad \text{(temporal clock: helicity } h = -\tfrac{1}{2}\text{)}\]

The two chiral clocks are permanently orthogonal and never mix. This
applies to massless spin-½ fermions (idealized neutrinos before mass
discovery).

\textbf{Photons are not described by this section.} Photons are spin-1
vector bosons governed by Maxwell's equations, not by the Dirac/Weyl
equation. Their two polarization states arise from gauge invariance
reducing the four components of \(A^\mu\) to two transverse degrees of
freedom --- \emph{not} from chiral Weyl decoupling. The structural
similarity (two decoupled helicity clocks) does exist when Maxwell is
rewritten in Riemann--Silberstein form
\(\mathbf{F} = \mathbf{E} + i\mathbf{B}\); see Paper §5 for the photon
treatment.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{6. Higgs Field as Kuramoto
Synchronizer}\label{higgs-field-as-kuramoto-synchronizer}

The Yukawa interaction written in Weyl (clock) form:

\[\frac{d\varphi_L}{dt} = \omega + K \sin(\varphi_R - \varphi_L + \delta_{\text{CP}})\]

\[\frac{d\varphi_R}{dt} = \omega + K \sin(\varphi_L - \varphi_R - \delta_{\text{CP}})\]

where the \textbf{Kuramoto coupling constant equals the fermion mass}:

\[\boxed{K = y_f \cdot \frac{v}{\sqrt{2}} = m_f}\]

with \(y_f\) the Yukawa coupling and \(v = 246\,\text{GeV}\) the Higgs
vacuum expectation value.

\begin{itemize}
\tightlist
\item
  \(K = 0\) (no Higgs): \(\varphi_L\) and \(\varphi_R\) free-run,
  \(\theta_{\text{rel}} = \pi/2\) --- massless
\item
  \(K > 0\) (Higgs): clocks synchronize, \(\theta_{\text{rel}} < \pi/2\)
  --- massive
\item
  Large \(K\) (top quark, \(y_f \approx 1\)): fast sync, tight lock
\item
  Small \(K\) (electron, \(y_f \approx 3 \times 10^{-6}\)): slow sync,
  loose lock
\end{itemize}

\subsubsection{Pair-sync at gauge
vertices}\label{pair-sync-at-gauge-vertices}

The Yukawa-style structure extends from intra-spinor (Higgs-mediated,
\(K = m\)) to inter-spinor (gauge-mediated): a dimensionless gauge
coupling times the local amplitude of the mediating field gives the
pair-sync rate at an interaction vertex.

\[\boxed{K_{\text{pair}}^{ab} = g_{\text{int}} \cdot \langle V_{\text{int}} \rangle_{\text{local}}}\]

with \(g_{\text{int}}\) the relevant gauge coupling (\(e\) for EM,
\(g_w\) for weak) and \(\langle V_{\text{int}} \rangle_{\text{local}}\)
the gauge-field amplitude at the partner's worldline. For
photon--electron:

\[K_{\text{pair}}^{\gamma e} = e \cdot |A_\gamma|_e \;\sim\; \hbar\omega\]

(sync timescale \(\tau_1 = \hbar/K_{\text{pair}} \sim 1/\omega\) --- the
photon's own period).

\textbf{Two-stage measurement Lagrangian.} Combining vertex pair-sync
(Stage 1) with bulk relaxation (Stage 2):

\[\mathcal{L}_{\text{detect}} = \underbrace{-K_{\text{pair}}\sin(\phi_\gamma - \phi_e)}_{\text{Stage 1: }\gamma\leftrightarrow e} \;-\; \underbrace{\Gamma_{\text{bulk}}\sin(\phi_e - \Phi_{\text{bulk}})}_{\text{Stage 2: }e\leftrightarrow\text{lattice}}\]

The framework now carries three Kuramoto couplings, each at a different
scale:

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.3333}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.3333}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.3333}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Coupling
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Origin
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Role
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
\(K = m\) & Higgs--Yukawa & intra-spinor L--R sync \\
\(K_{\text{pair}} = g_{\text{int}}\langle V_{\text{int}}\rangle\) &
gauge interaction & pair-sync at vertex (Stage 1) \\
\(\Gamma_{\text{bulk}} = GM^2/(\hbar\Delta z)\) & gravity + atomic &
bulk re-equilibration (Stage 2) \\
\end{longtable}
}

See Paper §3.4 for the full two-stage measurement process and its Bell /
gravitational consequences.

\subsubsection{Antiparticles as reversed
clocks}\label{antiparticles-as-reversed-clocks}

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.3333}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.3333}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.3333}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Particle \(u(p)\)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Antiparticle \(v(p)\)
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Phase & \(e^{-iEt/\hbar}\) & \(e^{+iEt/\hbar}\) \\
Clock direction & Forward (\(+E\)) & \textbf{Reversed} (\(-E\)) \\
Large/small components & Temporal dominant & Spatial dominant
(swapped) \\
Sync equilibrium & \(\varphi_L - \varphi_R \to +\delta_{\text{CP}}\) &
\(\varphi_L - \varphi_R \to -\delta_{\text{CP}}\) \\
\end{longtable}
}

The matter-antimatter asymmetry from CP-violating synchronization:

\$\(\eta = \frac{N_{\text{matter}} - N_{\text{antimatter}}}{N_{\text{total}}} \approx \varepsilon \cdot \sin^2(\delta_{\text{CP}})\)

\subsubsection{Annihilation cross
section}\label{annihilation-cross-section}

The synchronization efficiency between a particle and its antiparticle
at the moment of encounter depends on their phase mismatch:

\(\sigma_{\text{ann}} \propto |\langle\psi_{\text{particle}}|\psi_{\text{antiparticle}}\rangle|^2 \propto 1 + \varepsilon\cos(\delta_{\text{CP}})\)

The small asymmetry \(\varepsilon\) accumulates over early-universe
interactions, seeding the observed baryon asymmetry
\(\eta \sim 10^{-9}\).

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{7. Gravity as Bulk Clock
Synchronization}\label{gravity-as-bulk-clock-synchronization}

\subsubsection{Clock rate in a gravitational
field}\label{clock-rate-in-a-gravitational-field}

Gravitational time dilation as clock frequency gradient (Schwarzschild
weak field):

\[\omega(\mathbf{x}) = \omega_\infty \sqrt{1 + \frac{2\Phi(\mathbf{x})}{c^2}} \approx \omega_\infty\!\left(1 + \frac{\Phi}{c^2}\right)\]

where \(\Phi = -GM/r\) is the Newtonian potential. Clocks run
\textbf{slower} near mass.

\subsubsection{Poisson equation = Kuramoto field
equation}\label{poisson-equation-kuramoto-field-equation}

\[\underbrace{\nabla^2 \Phi = 4\pi G \rho}_{\text{Poisson (gravity)}} \qquad \longleftrightarrow \qquad \underbrace{\nabla^2 \varphi_{\text{clock}} = -\rho\, K_{\text{grav}}}_{\text{Kuramoto field}}\]

The gravitational potential \textbf{is} the bulk clock synchronization
field. Objects fall because their internal clocks drift toward the
nearest large synchronized cluster.

The clock-synchronization force recovers Newton exactly:

\$\(a_{\text{clock}} = \frac{d\omega}{dr} \cdot \frac{c^2}{\omega_0} = \frac{GM}{r^2} \qquad \checkmark\)

\subsubsection{Gravitational bulk coupling rate
(pair-counted)}\label{gravitational-bulk-coupling-rate-pair-counted}

For a bulk of mass \(M\) composed of \(N\) atoms (each of mass
\(m_{\text{atom}} = M/N\)), each pair contributes a Kuramoto rate
\(K_{aa} \sim G\,m_{\text{atom}}^2/(\hbar\,r_{ij})\) via the framework's
\(K = E/\hbar\) identification (distinct from the vertex pair-sync
\(K_{\text{pair}}^{ab}\) of §6: \(K_{aa}\) is the gravitational rate
between two bulk atoms). Summing over the \(N(N-1)/2 \approx N^2/2\)
atomic pairs at characteristic internal separation \(\Delta z\):

\[\Gamma_{\text{grav}} \sim \frac{N^2}{2}\cdot \frac{G\,(M/N)^2}{\hbar\,\Delta z} \;\sim\; \boxed{\frac{G M^2}{\hbar\,\Delta z}}\]

The \(M^2\) scaling is a consequence of pair counting: each pair
contributes \(\sim K_{aa}\), there are \(\sim N^2\) pairs, and
\(m_{\text{atom}} = M/N\) enters quadratically per pair, giving total
\(\sim N^2 (M/N)^2 = M^2\).

For macroscopic objects (\(M \sim 1\,\text{kg}\),
\(\Delta z \sim 1\,\text{m}\)),
\(\Gamma_{\text{grav}} \sim 6\times10^{23}\,\text{rad/s}\) --- an
extremely fast coupling rate that explains why macroscopic detectors
maintain classical coherence. The \(M^2\) scaling ensures bulk objects
are locked far more strongly than microscopic particles. (See Paper §3.5
for the full derivation; Paper §5.5 for why \(\Gamma_{\text{grav}} = 0\)
for photons.)

\subsubsection{Penrose objective reduction as gravitational clock
decoherence}\label{penrose-objective-reduction-as-gravitational-clock-decoherence}

A particle in superposition \(|x_1\rangle + |x_2\rangle\) has its clock
running at two different rates. Accumulated phase difference:

\[\delta\varphi(t) = \bigl[\omega(x_1) - \omega(x_2)\bigr] \cdot t = \delta\omega \cdot t\]

Coherence of the superposition:

\[\mathcal{C}(t) = \cos\!\left(\frac{\delta\varphi(t)}{2}\right)\]

Collapse when \(\mathcal{C} \to 0\), i.e., \(\delta\varphi = \pi\):

\[\boxed{\tau_{\text{collapse}} = \frac{\pi\hbar}{E_G}, \qquad E_G = \frac{Gm^2}{\Delta x}}\]

This is the \textbf{Penrose formula}, derived here as gravitational
clock decoherence. No observer required.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{8. Twistor Theory
Connection}\label{twistor-theory-connection}

Penrose's twistor \(Z^\alpha = (\omega^A,\, \pi_{A'})\) maps to:

\[\omega^A \;\longleftrightarrow\; \psi_L \quad \text{(temporal clock)} \qquad \pi_{A'} \;\longleftrightarrow\; \psi_R \quad \text{(spatial clock)}\]

The \textbf{null twistor condition} (massless particle):

\[Z \cdot \bar{Z} = \omega^A\bar{\pi}_A + \bar{\omega}^{A'}\pi_{A'} = 0 \qquad \Longleftrightarrow \qquad \theta_{\text{rel}} = 90° \qquad \Longleftrightarrow \qquad m = 0\]

The \textbf{incidence relation} (how spacetime position couples the two
clocks):

\[\omega^A = i\, x^{AA'}\pi_{A'} \qquad \text{(massless)}\]

\[\omega^A = i\, x^{AA'}\pi_{A'} + m\,\eta^A \qquad \text{(massive: Higgs term)}\]

This is the Dirac equation in Weyl form. Gravity curves twistor space by
deforming the incidence relation --- changing how the temporal and
spatial clocks couple through the spacetime position \(x\).

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{9. Temperature as Clock Phase Distribution
Width}\label{temperature-as-clock-phase-distribution-width}

At temperature \(T\), atomic clocks have Gaussian phase noise around the
bulk:

\[P(\varphi) \propto \exp\!\left(-\frac{\hbar\omega\,\varphi^2}{2k_BT}\right) \qquad \text{(classical limit } k_BT \gg \hbar\omega\text{)}\]

Phase noise standard deviation:

\[\sigma_\varphi(T) = \sqrt{\frac{k_B T}{\hbar\omega}} \qquad \text{(classical)}, \qquad \sigma_\varphi(0) = \frac{1}{\sqrt{2}} \; \text{rad} \qquad \text{(zero-point floor)}\]

The \textbf{Planck blackbody spectrum} is the emission spectrum of this
distribution:

\[\langle n(\omega) \rangle = \frac{1}{e^{\hbar\omega/k_BT} - 1}\]

\[u(\omega, T) = \frac{\hbar\omega^3}{\pi^2 c^3} \cdot \frac{1}{e^{\hbar\omega/k_BT} - 1} + \underbrace{\frac{\hbar\omega^3}{2\pi^2 c^3}}_{\text{zero-point residual}}\]

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 2\tabcolsep) * \real{0.5000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 2\tabcolsep) * \real{0.5000}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Temperature
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Physical meaning
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
\(T = 0\) & All clocks synchronized --- zero-point residual only
(\(\sigma_\varphi = 1/\sqrt{2}\) rad) \\
\(T > 0\) & Clocks desynchronized --- thermal phase noise
\(\sigma_\varphi \propto \sqrt{T}\) \\
\(T \to \infty\) & Complete desynchronization \\
\end{longtable}
}

\textbf{Absolute zero is unreachable} because the zero-point residual
field (\(\frac{1}{2}\hbar\omega\) per mode) prevents complete
synchronization.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{10. Brownian Motion: An Open
Question}\label{brownian-motion-an-open-question}

Earlier drafts proposed that the Kuramoto framework reproduces the
Stokes-Einstein diffusion relation \(D = k_BT/(6\pi\eta r)\) by treating
each molecular collision as a phase-difference impulse
\(\delta p = K\,\delta\varphi\), summing the random walk, and extracting
an effective \(K\) by matching to experiment. We have removed that
derivation. It does not survive scrutiny.

The framework's central identification \(K = m\) (Section 6) gives \(K\)
the units of frequency (rad/s, Compton frequency \(mc^2/\hbar\)). For a
Brownian diffusion formula of the form
\(D = K^2\,\sigma_\varphi^2\,\tau_{\text{coll}}/(2m^2)\) to come out in
\(\mathrm{m}^2/\mathrm{s}\), \(K\) must enter with units of momentum
(kg·m/s). The two \(K\)'s are dimensionally distinct objects.

Numerical attempts to bridge them by physically motivated guesses for an
electron in water at 300 K ---
\(K = p_{\text{thermal}} = \sqrt{2 m k_B T}\), \(K = mc\) (Compton
momentum), \(K = m\,v_{\text{thermal}}\) --- yield \(D_{\text{clock}}\)
values that miss the empirical Stokes-Einstein
\(D \approx 10^{-9}\,\mathrm{m}^2/\mathrm{s}\) by 4 to 50 orders of
magnitude. There is no principled way for the framework's \(K = m\) to
reproduce molecular Brownian motion. Earlier drafts solved for \(K\) to
make the match work, which made the residual ``prediction''
\(D \propto 1/\sqrt{\omega}\) downstream of the fit rather than
independent.

The relationship between the framework's chiral phase clocks and
molecular Brownian motion is therefore an open question. Two routes for
future work:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Many-body Kuramoto reduction.} Derive an effective collisional
  coupling for a fermion in a thermal bath from the framework's
  \(K = m\) via a coarse-graining over many chiral-clock interactions,
  and check whether it can reproduce the friction coefficient
  \(\gamma = 6\pi\eta r\).
\item
  \textbf{Bound the framework's home regime.} Treat Brownian motion as
  outside the framework's natural scope (which is fermion chiral
  synchronization at the Compton scale), and rely on the Nelson
  stochastic-mechanics connection (Section 11) as the framework's
  appropriate touch-point with classical diffusion. The zero-point
  diffusion floor \(\nu_{\text{ZPF}} = \hbar/2m\) remains
  well-motivated; the molecular Brownian regime does not reduce to it.
\end{enumerate}

We retain Section 11's quantum-classical crossover discussion, which
rests on the standard Einstein--Smoluchowski \(D \sim k_B T\,\tau/m\)
rather than on any clock-fit derivation.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{11. Quantum-Classical
Transition}\label{quantum-classical-transition}

\subsubsection{Nelson's stochastic
mechanics}\label{nelsons-stochastic-mechanics}

Nelson (1966) proved that Brownian motion in a background field with
diffusion coefficient:

\[\nu = \frac{\hbar}{2m}\]

satisfies the \textbf{Schrödinger equation exactly}. The time-phase
model provides the physical field: the zero-point residual waves, with
quantum diffusion floor \(\nu_{\text{ZPF}} = \hbar/2m\).

Total diffusion (quantum + thermal):

\[\nu_{\text{total}} = \underbrace{\frac{\hbar}{2m}}_{\text{quantum (ZPF)}} + \underbrace{\frac{k_B T\,\tau}{m}}_{\text{thermal (Brownian)}}\]

\subsubsection{Quantum-classical
crossover}\label{quantum-classical-crossover}

The quantum-classical transition occurs when thermal clock noise
overtakes quantum clock noise:

\[\frac{k_B T\,\tau}{m} \gg \frac{\hbar}{2m} \qquad \Longrightarrow \qquad k_B T \gg \frac{\hbar}{2\tau}\]

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
System
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\(\hbar/2m\) (m²/s)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\(k_BT\tau/m\) at 300 K
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Regime
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Electron in atom (\(\tau \sim 10^{-15}\) s) & \(3\times 10^{-5}\) &
\(10^{-21}\) & \textbf{Quantum} \\
Proton (\(\tau \sim 10^{-13}\) s) & \(1.7\times 10^{-8}\) & \(10^{-18}\)
& Quantum \\
Protein (\(10^{-22}\) kg) & \(5\times 10^{-13}\) & \(10^{-14}\) &
Borderline \\
1 μm dust grain & \(10^{-22}\) & \(10^{-11}\) & \textbf{Classical} \\
\end{longtable}
}

The Schrödinger's cat boundary falls exactly where the Penrose collapse
time equals the thermal decoherence time:

\[\tau_{\text{Penrose}} = \frac{\pi\hbar\,\Delta x}{Gm^2} \quad \Longleftrightarrow \quad \tau_{\text{thermal}} = \frac{m}{k_B T\,\tau_{\text{coll}}}\]

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{12. The Born Rule as Energy
Partition}\label{the-born-rule-as-energy-partition}

In this framework, \(|\psi|^2\) is not fundamentally a probability ---
it is the \textbf{energy density} of the real oscillating field
\(\psi\). The probabilistic appearance of measurement outcomes reflects
unpredictable interference with the zero-point + thermal background
field at the moment of synchronization with the detector. The Born rule
is read as the long-run frequency of energy partition into the available
detector channels under unbiased stochastic background driving, not as
an independent probability axiom.

\subsubsection{Wave energy as the primary
quantity}\label{wave-energy-as-the-primary-quantity}

For a superposition \(\psi = \alpha|0\rangle + \beta|1\rangle\) in the
wave-realist reading,

\[E_0 \propto |\alpha|^2, \qquad E_1 \propto |\beta|^2\]

are the \textbf{energy fractions} carried by each channel. This is
classical wave physics --- no Born postulate is required to write down
these quantities.

\subsubsection{Energy-partition
mechanism}\label{energy-partition-mechanism}

A Kuramoto re-synchronization event transfers wave energy from the
particle to one detector channel, raising it to its excited (registered)
state. A discrete click --- rather than a fractional excitation across
multiple channels --- arises because each detector channel is itself a
quantized resonator with a discrete excitation threshold.

Which channel receives the quantum in any individual event depends on
the instantaneous configuration of the background field at the moment of
contact. Because the background fluctuations are statistically unbiased
on the channel-selection phase space (zero-point symmetry; unbiased
thermal noise), long-run frequencies of channel selection converge to
the energy fractions:

\[\boxed{P(|0\rangle) = |\alpha|^2, \qquad P(|1\rangle) = |\beta|^2}\]

read here as long-run \emph{frequencies of energy partition} rather than
as a probability axiom of quantum theory.

\subsubsection{Connection to Nelson stochastic
mechanics}\label{connection-to-nelson-stochastic-mechanics}

Nelson (1966) {[}26{]} showed that a real particle undergoing stochastic
motion in a background field with diffusion coefficient
\(\nu = \hbar/(2m)\) satisfies the Schrödinger equation. The framework
supplies a physical identity for that background --- the zero-point
residual of the chiral phase clocks (Section 9) --- and reads the Born
rule as the visible energy-partition statistics under that background's
stochastic driving.

\subsubsection{Honest limitation}\label{honest-limitation}

The reframing replaces the standard Born axiom with a weaker postulate
set (wave realism + unbiased background) but does not yet derive that
the bias-free assumption is exact across the channel-selection phase
space. This is a future-work item, not a settled result. The framework
is structurally a hidden-variable theory in which the hidden variable is
the instantaneous background-field configuration; it satisfies Bell's
theorem because it does not use this story to explain Bell correlations
(those come from the full Dirac spinor structure, Section 4 of this
reference).

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{13. Heisenberg Uncertainty as the Fourier Bandwidth
Theorem}\label{heisenberg-uncertainty-as-the-fourier-bandwidth-theorem}

In MCI's wave-realist reading, the wavefunction \(\psi\) is a real
oscillating field, and conjugate representations are related by Fourier
transform via the de Broglie/Planck relations \(p = \hbar k\),
\(E = \hbar\omega\). The \textbf{Fourier bandwidth theorem} of harmonic
analysis --- rigorous and independent of any quantum interpretation ---
gives the uncertainty relations directly, with factor of ½ exact.

\subsubsection{Position-momentum}\label{position-momentum}

For \(\psi(x) \in L^2(\mathbb{R})\) with Fourier transform
\(\varphi(k)\):

\[\sigma_x \cdot \sigma_k \geq \frac{1}{2}\]

Multiplying by \(\hbar\) via \(p = \hbar k\):

\[\boxed{\sigma_x \cdot \sigma_p \geq \frac{\hbar}{2}}\]

Saturated by Gaussian wavepackets. This is the Heisenberg
position-momentum uncertainty relation derived as a theorem about real
waves, not postulated as an axiom about operators.

\subsubsection{Energy-time}\label{energy-time}

The same theorem applied to the temporal wavefunction \(\psi(t)\) and
its Fourier transform in frequency:

\[\sigma_t \cdot \sigma_\omega \geq \frac{1}{2} \;\Longrightarrow\; \boxed{\sigma_E \cdot \sigma_t \geq \frac{\hbar}{2}}\]

via \(E = \hbar\omega\). Same theorem, conjugate variables.

\subsubsection{Zero-point phase floor as the same theorem in chiral
variables}\label{zero-point-phase-floor-as-the-same-theorem-in-chiral-variables}

The zero-point phase noise (Section 9):

\[\sigma_\varphi(0) = \frac{1}{\sqrt{2}}\;\text{rad}\]

is the Fourier bandwidth theorem applied to the chiral phase clocks
themselves --- the minimum joint uncertainty in conjugate phase
variables is ½ in natural units. The zero-point energy
\(\tfrac{1}{2}\hbar\omega\) per mode is the energy cost of saturating
this minimum phase uncertainty. The uncertainty principle and the
zero-point field are the same statement in different variables.

\subsubsection{\texorpdfstring{Mixing angle \(\theta_{\text{rel}}\) as
which-clock-dominates
indicator}{Mixing angle \textbackslash theta\_\{\textbackslash text\{rel\}\} as which-clock-dominates indicator}}\label{mixing-angle-theta_textrel-as-which-clock-dominates-indicator}

The Dirac mixing angle satisfies

\[\tan\frac{\theta_{\text{rel}}}{2} = \frac{|\mathbf{p}|}{E + m}\]

At rest (\(\theta_{\text{rel}} \to 0\)) the temporal clock dominates; at
ultrarelativistic speeds (\(\theta_{\text{rel}} \to \pi/2\)) the spatial
clock dominates. The two limits are the geometric expression of Fourier
complementarity in the chiral basis: localizing one clock at the cost of
the other, with the conjugate uncertainty saturating the universal
Fourier bound.

\subsubsection{Compton wavelength: a particle-specific scale, NOT the
source of
½}\label{compton-wavelength-a-particle-specific-scale-not-the-source-of-uxbd}

The Compton wavelength \(\lambda_C = h/(mc)\) is a particle-specific
scale at which the two-clock structure becomes manifest (Zitterbewegung,
pair production, chiral mixing). It is \textbf{not} the source of the
\(\hbar/2\) in the uncertainty relation --- that \(\hbar/2\) is
universal, particle-independent, and follows from the Fourier theorem
alone, applying equally to electrons and to baseballs.

A heavier particle has a faster clock (higher Compton frequency) and
therefore a smaller characteristic length below which its internal clock
structure becomes resolvable. But the \emph{uncertainty bound}
\(\sigma_x \sigma_p \geq \hbar/2\) applies identically to all particles.
The Compton scale and the Fourier bound are different facts about the
wavefunction; conflating them was an error in earlier formulations.

\subsubsection{The commutator as the operator-level Fourier
theorem}\label{the-commutator-as-the-operator-level-fourier-theorem}

The canonical commutation relation

\[[\hat{x}, \hat{p}] = i\hbar\]

is the operator-level expression of the Fourier bandwidth theorem:
\(\hat{x}\) and \(\hat{p}\) are Fourier-conjugate operators, and the
imaginary unit reflects the \(\pi/2\) phase shift between conjugate
Fourier variables. In MCI's chiral picture, this corresponds to the
maximum complementarity (\(\theta_{\text{rel}} = \pi/2\)) between the
temporal and spatial clocks --- the geometric expression of the same
harmonic-analytic content.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{14. Complete Dictionary}\label{complete-dictionary}

\$\(\begin{array}{lll}
\textbf{Time-phase model} & \textbf{Standard physics} & \textbf{Geometric (Twistor)} \\
\hline
\text{Temporal clock } \psi_L\,^{*} & \text{Left Weyl spinor} & \omega^A \\
\text{Spatial clock } \psi_R\,^{*} & \text{Right Weyl spinor} & \pi_{A'} \\
\text{L-R coupling} = m & \text{Dirac mass term} & \text{Non-null: } Z\cdot\bar{Z} \neq 0 \\
\theta_{\text{rel}} = 90° & \text{Massless particle} & \text{Null twistor} \\
\text{Higgs synchronizer} & \text{Yukawa coupling} & \text{Twistor cohomology} \\
\text{Gravity} = \nabla^2\varphi_{\text{clock}} & \text{Newtonian potential} & \text{Twistor space curvature} \\
\text{Penrose collapse} & \text{Wavefunction collapse} & \delta\varphi = \pi \\
\text{Temperature} & k_BT & \sigma_\varphi^2 = k_BT/\hbar\omega \\
\text{Zero-point field} & \tfrac{1}{2}\hbar\omega\text{ per mode} & \sigma_\varphi(0) = 1/\sqrt{2} \\
\text{Antiparticle} & e^{+iEt/\hbar} & \text{Reversed clock} \\
\text{Matter asymmetry} & \text{Baryogenesis} & \eta \approx \varepsilon\sin^2\delta_{\text{CP}} \\
\text{Born rule } P = |\psi|^2 & \text{Postulated} & |\psi|^2 = \text{wave energy density; freq.\ stat.\ under unbiased background} \\
\text{Uncertainty principle} & \Delta x\,\Delta p \geq \hbar/2 & \text{Fourier bandwidth theorem on real }\psi\text{; chiral phases }\delta\varphi_L\,\delta\varphi_R \geq \tfrac{1}{2} \\
\text{Measurement} & \text{Wavefunction collapse} & \text{Kuramoto re-sync to bulk} \\
\text{Entanglement} & \text{Non-separable state} & \text{Synchronized clocks at creation: } \varphi_A = \varphi_B \\
\text{Bell's theorem} & \text{No local HV model} & \Phi_{\text{bulk}} \text{ shared} \Rightarrow \text{factorization fails} \\
\text{Quantum-classical} & \text{Decoherence} & k_BT\tau/m \gg \hbar/2m \\
\text{Nelson stochastic QM} & \nu = \hbar/2m & \text{Zero-point field diffusion} \\
\text{Zitterbewegung} & \omega = 2mc^2/\hbar & \text{L-R clock beat frequency} \\
\text{Spin-statistics sign} & \text{Pauli antisymmetry} & \chi \to -\chi \text{ under } 2\pi \text{ rotation (SU(2) double cover)} \\
\text{Microcausality} & [\psi(x),\psi(y)]_\pm = 0,\ (x-y)^2<0 & \text{Sync manifold respects the light cone} \\
\end{array}\)

\emph{* Identification is exact in the Weyl basis. In the Dirac/standard
basis the temporal-phase content is a θ\_rel-dependent combination of
upper and lower blocks; see §0.}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{15. Zitterbewegung as Clock Beat
Frequency}\label{zitterbewegung-as-clock-beat-frequency}

Zitterbewegung --- the rapid trembling motion of a free Dirac particle
--- is the beat note between the temporal and spatial phase clocks.

The temporal clock oscillates at \(\omega_t = E/\hbar\); the spatial
clock at \(\omega_s = p^2/(m\gamma\hbar)\). Their beat frequency in the
non-relativistic limit:

\(\boxed{\omega_{\text{Zitter}} \approx \frac{2mc^2}{\hbar}}\)

This is the known Zitterbewegung frequency, here derived as the beat
note between two coupled oscillators rather than as interference between
positive- and negative-frequency Dirac solutions.

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Mass regime
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\(K = m\)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Clock behavior
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Zitterbewegung
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Massless (\(m = 0\)) & \(0\) & Permanently decoupled,
\(\theta_{\text{rel}} = 90°\) & None --- consistent with photons \\
Light particle (small \(m\)) & Small & Loose synchronization & Large
amplitude \\
Heavy particle (large \(m\)) & Large & Fast, tight lock & Small
amplitude \\
\end{longtable}
}

The Zitterbewegung frequency is the Compton frequency
\(\omega_C = mc^2/\hbar\) --- the same rate that sets the Nyquist
spatial bandwidth limit in Section 13 and the synchronization timescale
\(\tau_{\text{sync}} = 1/K = \hbar/mc^2\).

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{16. Spin-Statistics from the Chiral
Pair}\label{spin-statistics-from-the-chiral-pair}

The Madelung-style polar decomposition of each Weyl spinor splits the
wave function into three layers:

\[\boxed{\psi_{L,R} = \rho_{L,R}^{1/2}\, e^{i\phi_{L,R}}\, \chi_{L,R}}\]

with \(\rho_{L,R} \geq 0\) a real amplitude density, \(\phi_{L,R}\) a
real phase mod \(2\pi\) (the Kuramoto clock variable), and
\(\chi_{L,R}\) a unit two-spinor frame in the SU(2) representation. Of
the three, only \(\chi_{L,R}\) lives in a representation where a sign
can appear under \(2\pi\) rotation.

\subsubsection{Rotation operator}\label{rotation-operator}

For the Dirac 4-spinor in the standard basis with
\(\Sigma = \mathrm{diag}(\boldsymbol{\sigma},\boldsymbol{\sigma})\):

\[U(\theta,\hat{n}) = \exp\!\left(-i\,\theta\,\boldsymbol{\Sigma}\cdot\hat{n}/2\right), \qquad U(2\pi,\hat{n}) = -\mathbb{1}_{4\times 4}\]

\subsubsection{\texorpdfstring{Sign under \(2\pi\) rotation by
representation}{Sign under 2\textbackslash pi rotation by representation}}\label{sign-under-2pi-rotation-by-representation}

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.3333}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.3333}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.3333}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Object
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Representation
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\(\langle\psi|U(2\pi)|\psi\rangle\)
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Scalar & trivial & \(+1\) \\
Vector (spin 1) & SO(3), integer & \(+1\) \\
Weyl 2-spinor (single chirality) & SU(2), spin-½ & \(-1\) \\
Dirac 4-spinor (chiral pair) &
\((\tfrac{1}{2},0)\oplus(0,\tfrac{1}{2})\) & \(-1\) \\
\end{longtable}
}

By the Feynman-Finkelstein argument, exchange of two identical particles
in 3+1D is continuously homotopic to a \(2\pi\) rotation of one of them,
so the sign of the rotation overlap is the sign of the exchange
amplitude. The chiral pair the framework already commits to (for
\(K=m\)) is precisely the spin-½ representation that forces fermion
antisymmetry. The Kuramoto ODE for \((\phi_L,\phi_R)\) acts on
real-valued phases and is exchange-symmetric --- the fermion sign is in
\(\chi_{L,R}\), not in \(\phi_{L,R}\) or \(\rho_{L,R}\).

\subsubsection{Microcausality}\label{microcausality}

For two field events at spacelike separation:

\[\boxed{[\psi(x),\psi(y)]_\pm = 0 \quad \text{for}\quad (x-y)^2 < 0}\]

(commutator for bosons, anticommutator for fermions). MCI reading: no
chain of Kuramoto sync events has connected the clocks at \(x\) and
\(y\); their structures are independent in the synchronization manifold.
The choice of sign in the (anti)commutator is forced by the same SU(2)
double-cover fact above --- it is one structural fact, not two.

See Appendix D of the main paper and \texttt{spin\_statistics.py} for
numerical verification (six tests, including a momentum scan over six
decades that confirms the sign is unaffected by the relativistic
large/small mixing of Appendix A).

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{Generated from conversations between a radiologist and Claude
(Anthropic). Mathematical framework developed by AI; physical intuitions
by the author.}

\end{document}
